Greenhouse gas emissions model - making scenarios

### 2022-05-11 Scenarios_report.Rmd
scenarios - added first version of probability of emissions reduction for milk yield increases

```{r, warning=FALSE, include=FALSE}
#install and load packages
library(DiagrammeR)
# devtools::install_github("eikeluedeling/decisionSupport")
library(decisionSupport)
library(ggplot2)
library(kableExtra)
library(magrittr)
library(plyr)
library(rmarkdown)
# devtools::install_github("CWWhitney/uncertainty")
library(uncertainty)
library(chillR)

@@

# the following isn't working yet
# I suspect this is because of an error in the varslice_resample function (and also the varkernelslice functions).
# I suspect the problem is in   Relative_probability <- in_outkernel$z[, expectedin_var]
# There may not be an expectedin_var'th column - this should be the column that corresponds to the x value expectedin_var

while (more_milk < max(in_var))
{
  more_milk <- more_milk + 10
  slice_more_milk <-
    varslice_resample(in_var,
                      out_var,
                      expectedin_var = more_milk,
                      n_runs = 100000)
  results <-
    rbind(results, c(more_milk, sum(sliceb > slice_more_milk) / length(sliceb)))
}

>>>>

```{r, warning=FALSE, include=FALSE}
#install and load packages
library(DiagrammeR)
# devtools::install_github("eikeluedeling/decisionSupport")
library(decisionSupport)
library(ggplot2)
library(kableExtra)
library(magrittr)
library(plyr)
library(rmarkdown)
# devtools::install_github("CWWhitney/uncertainty")
library(uncertainty)
library(chillR)
library(raster)

@@

#devtools::install_github("CWWhitney/uncertainty")
#require(uncertainty)

?varslice_resample

milk_yields_to_sample<-seq(100,10000,100)
milk_yields_to_sample<-milk_yields_to_sample[which(milk_yields_to_sample<max(in_var))]
slices<-list()

# slice through the distribution at every 100 L milk yield per cow

for(i in 1:length(milk_yields_to_sample))
{slices[[i]]<-
  varslice_resample(in_var,
                      out_var,
                      expectedin_var = milk_yields_to_sample[i],
                      n_runs = 100000,
  out_var_sampling = (max(out_var) - min(out_var))/10000)$resample
 }

#decreased_emissions_probability <-
#  data.frame(Base_yield = milk_yields_to_sample)#
#
#for (i in 1:(length(milk_yields_to_sample) - 1))
#{
#  for (j in (i + 1):length(milk_yields_to_sample))
#    decreased_emissions_probability[i, j] <-
#      sum(slices[[i]] > slices[[j]]) / length(slices[[i]])
#  
#}
#colnames(decreased_emissions_probability)[2:ncol(decreased_emissions_probability)] <-
#  paste0("new", milk_yields_to_sample[2:length(milk_yields_to_sample)])

decreased_emissions_probability2 <-
  data.frame(Base_yield = NA,new_yield=NA,probability=NA)

for (i in 1:(length(milk_yields_to_sample) - 1))
{
  for (j in (i + 1):length(milk_yields_to_sample))
    {decreased_emissions_probability2[nrow(decreased_emissions_probability2)+1,"Base_yield"]<-milk_yields_to_sample[i]
     decreased_emissions_probability2$new_yield[nrow(decreased_emissions_probability2)]<-milk_yields_to_sample[j]
     decreased_emissions_probability2$probability[nrow(decreased_emissions_probability2)] <-
      sum(slices[[i]] > slices[[j]]) / length(slices[[i]])

}
}

decreased_emissions_probability2<-decreased_emissions_probability2[which(!is.na(decreased_emissions_probability2$Base_yield)),]

decreased_emissions_probability2[,"yield_increase"]<-decreased_emissions_probability2$new_yield-decreased_emissions_probability2$Base_yield

ggplot(data = decreased_emissions_probability2, aes(Base_yield, yield_increase, z =
                                                      probability)) + geom_contour_filled() +
  ggtitle("Probability that emission reductions occurred") + 
  xlab("Baseline milk yield per head and year (kg)") +
  ylab("Milk yield increase per head and year (kg)") +
  stat_contour(breaks = c(0.9),col="black")
